A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-08-26 rr-flow.Rmd
fix typo

Windows has the bigest hurdle to install what is needed. However there is a great package manager for Windows called chocolately which you can install from: [https://chocolatey.org](https://chocolatey.org).
After having installed chocolately, all dependencies can be installed in an **admin terminal** via:

```{bash, eval=FALSE}
choc install git make docker-desktop
```

>>>>

Windows has the bigest hurdle to install what is needed. However there is a great package manager for Windows called chocolately which you can install from: [https://chocolatey.org](https://chocolatey.org).
After having installed chocolately (and restarted the computer), all dependencies can be installed in an **admin terminal** via:

```{bash, eval=FALSE}
choco install git make docker-desktop
```
